API design for machine learning software: experiences from the scikit-learn project

### 2013-06-25 paper.tex
Reword task to algorithm

The \sklearn project \citep{pedregosa2011} is an open source machine learning
library for the Python programming language. The ambition of the project is to
provide efficient and well-established machine learning tools within a
programming environment that is accessible to non-machine learning experts and
reusable in various scientific areas. The project is not a novel domain-specific
language, but a library that provides machine learning idioms to a general-
purpose high-level language. Among other things, it includes classical learning
algorithms, model selection tools and preprocessing procedures. The project is
distributed under the simplified BSD license, encouraging its use in both
academic and commercial settings.

@@

\section{Future Work}
\label{sec:future_work}
There are several problems with the current scikit-learn interface which
will be resolved in the future.
At present, the library does not support some classical machine learning tasks,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
Tasks like structured prediction or reinforcement learning are
considered off-scope for the project, since they would require quite different
data representations and APIs.

>>>>

The \sklearn project\footnote{\url{http://scikit-learn.org}}
\citep{pedregosa2011} is an open source machine learning
library for the Python programming language. The ambition of the project is to
provide efficient and well-established machine learning tools within a
programming environment that is accessible to non-machine learning experts and
reusable in various scientific areas. The project is not a novel domain-specific
language, but a library that provides machine learning idioms to a general-
purpose high-level language. Among other things, it includes classical learning
algorithms, model selection tools and preprocessing procedures. The project is
distributed under the simplified BSD license, encouraging its use in both
academic and commercial settings.

@@

\section{Future work}
\label{sec:future_work}
There are several problems with the current scikit-learn interface which
will be resolved in the future.
At present, the library does not support some classical machine learning
algorithms,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
Tasks like structured prediction or reinforcement learning are
considered off-scope for the project, since they would require quite different
data representations and APIs.
